Exp1 - Opt w_max and {A,phi)

### 2018-03-11 voltagebudget/analysis/paper_figures.Rmd
Updating paper figs (in progress)

# Voltage budget timecourse

```{r}
vms <- read_csv("vm_comp_timecourse.csv")
```

```{r, fig.width=1.5, fig.height=1.3}
vms %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=vm)) +
  geom_ribbon(fill="blue", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  labs(x="", y="Vm") +
  theme_classic() -> p1

vms %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
  # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
  # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
  labs(x="Times (s)", y="") +
  theme_classic() -> p2

vms %>% 
  filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  # geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  # geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3),  fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  labs(x="", y="") +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p3

plot_grid <- rbind(c(1 , 1, NA), c(2, 2, 3))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
```

# Bounds

```{r, message=FALSE, fig.width=1.5, fig.height=1.3}
name <- "../data/exp7_d-2e-3_f20.csv"
results <- read_csv(paste(name, sep=""))

results %>% 
  filter(V_free > 0.002) %>% 
  ggplot(aes(x=V_free*1e3)) +
  geom_histogram(aes(y=0.5*..density..), bins=50, size=0.2) +
  geom_density(alpha=0.3, fill="black") +
  geom_vline(aes(xintercept=min(1e3*V_free - 0.05)), color="darkolivegreen3", alpha=0.6) +
  geom_vline(aes(xintercept=max(1e3*V_free + 0.01)), color="goldenrod2", alpha=0.5) +
  labs(x="V_free (mvolt)", y="Density (AU)") +
  xlim(3, 6) +
  theme_classic() -> p1

results %>% 
  filter(V_free > 0.002) %>% 
  ggplot(aes(x=variances, y=errors, color=V_free)) +
  geom_point(alpha=0.5) +
  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
  theme_classic() -> p2
```

```{r, message=FALSE, fig.width=3, fig.height=1.7}
# Load min, max V_free and neighbors
name <- "../data/exp5_d-2e-3_f8_r1.csv"
rank1 <- read_csv(paste(name, sep=""))
rank1$rank <- rep(1, nrow(rank1))

name <- "../data/exp5_d-2e-3_f8_r2.csv"
rank2 <- read_csv(paste(name, sep=""))
rank2$rank <- rep(2, nrow(rank2))

name <- "../data/exp5_d-2e-3_f8_r3.csv"
rank3 <- read_csv(paste(name, sep=""))
rank3$rank <- rep(3, nrow(rank3))

name <- "../data/exp5_d-2e-3_f8_r50.csv"
rank50 <- read_csv(paste(name, sep=""))
rank50$rank <- rep(50, nrow(rank50))

name <- "../data/exp5_d-2e-3_f8_r49.csv"
rank49 <- read_csv(paste(name, sep=""))
rank49$rank <- rep(49, nrow(rank49))

name <- "../data/exp5_d-2e-3_f8_r48.csv"
rank48 <- read_csv(paste(name, sep=""))
rank48$rank <- rep(48, nrow(rank48))

# Group 'em
ranked <- rbind(rank1, rank2, rank3, rank50, rank49, rank48)

# -----------------------------------------------------
# TODO: manual color assignment, setting alphas to rank?
ranked %>%
  ggplot(aes(x=N, y=sort(errors), color=rank, group=rank)) +
  geom_line(alpha=0.4) +
  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
  theme_classic() -> p3

ranked %>%
  ggplot(aes(x=N, y=sort(variances), color=rank, group=rank)) +
  geom_line(alpha=0.4) +
  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
  theme_classic() -> p4

plot_grid <- rbind(c(1 , 1, NA, 3, 3, 3), c(2, 2, 2, 4, 4, 4))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
```

# Pareto opt
```{r, message=FALSE, fig.width=2.2, fig.height=1.9}
name <- "../data/exp4_d-2e-3_f12.csv"
results <- read_csv(paste(name, sep=""))

results %>% 
  # filter(errors < 0.6, variances > 0) %>%
  ggplot(aes(y=V_comp*1e3, x=V_osc*1e3, color=As)) +
  scale_color_gradient(low="mediumpurple", high="red3", name="A") +
  xlab("Vc (mvolt)") + ylab("Vo (mvolt)") +
  geom_point(alpha=0.4) + 
  theme_classic() + 
  theme(legend.position="bottom", legend.key.size =  unit(0.3, "in")) -> p1

results %>% 
  ggplot(aes(x=1e3*V_free, y=normalize(variances))) +
  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
  # geom_point(color="red3", alpha=0.2) + 
  geom_smooth(aes(x=1e3*V_free, y=normalize(errors)), 
              method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", se=FALSE,linetype="dashed") + 
  # geom_point(aes(x=1e3*V_free, y=normalize(errors)), color="mediumpurple", alpha=0.2) + 
  geom_vline(aes(xintercept = mean(1e3*V_free)), color="black") +
  xlab("Vf (mvolt)") +
  ylab("Normalized") +
  theme_classic() -> p2

results %>% 
  ggplot(aes(x=1e3*V_comp, y=errors)) +
  geom_point(alpha=0.4, size=.3, color="mediumpurple") +
  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", alpha=0.2, se=FALSE, linetype="dashed") + 
  xlab("Vc (mvolt)") +
  ylab("Errors (s)") +
  theme_classic() -> p3

results %>% 
  ggplot(aes(x=1e3*V_osc, y=variances)) +
  geom_point(alpha=0.3, size=.3, color="red3") +
  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
  xlab("Vo (mvolt)") +
  ylab("Variance (s)") +
  theme_classic() -> p4

plot_grid <- rbind(c(NA ,NA, 3, 3), c(NA, NA, 3, 3), c(NA, NA, 4, 4), c(1 ,1, 4, 4), c(1, 1, 2, 2), c(1, 1, 2, 2))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
```

# Voltage timecourses many neurons

```{r}
vms <- read_csv("vm_full_examples.csv")
vms <- gather(vms, "neuron", "vm", 2:21)
wins <- read_csv("vm_window_examples_d2_w2.csv")
wins <- gather(wins, "neuron", "vm", 2:21)
```

```{r, fig.width=1.5, fig.height=1}
vms %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, y=vm, group=neuron)) +
  geom_line(color="black", alpha=0.3, size=0.2) +
  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
  labs(x="Time (s)", y="Vm (mV)") +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.25) +
  geom_hline(yintercept=-70e-3, color="black", size=2) +
  geom_vline(xintercept = 0.25719 + 2e-3, color="darkgreen", alpha=0.5, size=0.2) +
  geom_vline(xintercept = 0.25719 + 2e-3 +  0.03333333, color="darkgreen", alpha=0.5, size=0.2) +
  theme_classic()
```
```{r, fig.width=0.4, fig.height=0.8}
vms %>% 
  filter(t > 0.25, t < 0.27) %>%
  ggplot(aes(x=t, y=vm, group=neuron)) +
  geom_line(color="black", alpha=0.3, size=0.2) +
  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
  labs(x="Time (s)", y="Vm (mV)") +
  geom_hline(yintercept=-50e-3, color="black", linetype="dashed", size=1) +
  geom_hline(yintercept=-70e-3, color="black", size=2) +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank())
  # theme_classic()
```

>>>>

# Read and process all data

```{r, message=FALSE}
# -
# Example voltage timecourses
results0 <- read_csv("vm_comp_timecourse.csv")

# -
# Sweep A
exp <- "72"
freqs <- c(8, 12, 20, 30)

# Load
results1 <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

  df$freq <- rep(freq, nrow(df))
  results1 <- rbind(results1, df)
}

# Process
results1 %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results1

rm(df, exp, freq, freqs, name)
```

# Budget intro

```{r, fig.width=1.5, fig.height=1.3}
results0 %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=vm)) +
  geom_ribbon(fill="blue", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  labs(x="", y="Vm") +
  theme_classic() -> p1

results0 %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
  # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
  # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
  labs(x="Times (s)", y="") +
  theme_classic() -> p2

results0 %>% 
  filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  # geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  # geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3),  fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  labs(x="", y="") +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p3

plot_grid <- rbind(c(1 , 1, NA), c(2, 2, 3))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

# Trade-off

```{r, fig.width=1.3, fig.height=1.9}
results1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As*1e9, y=errors_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="A (namp)", y="Error (ms)") +
  theme_classic() +
  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
  theme(legend.position="none") -> p1

results1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="A (namp)", y="Variance (ms)") +
  lims(y=c(0, 12)) +
  theme_classic() +
  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
  theme(legend.position="right") -> p2

results1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
  theme(legend.position="none") +
  labs(x="Error (ms)", y="Variance (ms)") -> p3

plot_grid <- rbind(c(1, 1, NA), c(2, 2, 2), c(3, 3, NA))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
```

# Bound 1 - V_osc/V_comp (f = 20)

```{r, fig.width=1.25, fig.height=1.15}
results1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=As*1e9, y=1e3*V_osc)) +
  geom_point(size=0.1, alpha=0.01) + 
  labs(x="A (namp)", y="V_osc (mvolt)") +
  theme_classic() -> p1

plot_grid <- rbind(c(1))
grid.arrange(p1, layout_matrix=plot_grid)
```
